TacticToe: Learning the Game of Tactics

### 2018-01-16 tactictoe_jv.tex
Proof presentation: update

\section{Proof Presentation}\label{sec:proofdisplay}\todo{MN + RK: add 
motivations and transitions + review}

>>>>

\section{Proof Presentation}\label{sec:proofdisplay}\todo{MN + RK: add 
motivations and transitions}

Motivation: 
+ minimal effort to integrate the tactictoe results in proof scripts.

Side effect:
+ could be also used to simplify existing proof scripts.
